---
title: Data Frame Manipulation
author: Li Fu
date: '2019-10-10'
slug: Data Frame manipulation
categories:
  - Stats 101
tags:
  - mean
  - variance
---
Last post made me very sad, waste 2 hours about package"xlsx" still failed, very frustrated.

<p>Okay, this post is basic idea of data frame manipulation, terminal command lines is too difficult for me.</p>

### get sample dataset from R

R has sample dataset in package ‘datasets’, following line will return the list of those dataset.
   
```{r, warning=FALSE, eval=FALSE}
data()
```

### load in data
I'm gonna use this one: trees, Diameter, Height and Volume for Black CherryTrees

```{r}
## it seems this line has no meaning, we don't really need it
data("trees")
```

### data overview
```{r}
## save as a data frame
df <- trees

## check structure of df
head(df)
```
dimension of df
```{r}
dim(df)
```

row number= 31, column number = 3.

<p>data fromat</p>
```{r}

str(df)
```
all three columns are numerical 

### column names
```{r}
colnames(df)
```
### row names
```{r}
rownames(df)
```
Sometimes, some dataset has row names


### select one row
select row 1
```{r}
df[1,]
```

### select multiple rows
select row 1 and 3
```{r}
df[c(1,3),]
```

### select one column
select column1
<em><p>METHOD1:</P></em>
```{r}
df[,1]
```

<em><p>METHOD2:</P></em>
```{r}
df$Girth
```

### select multiple columns
select column 1 and column 2
```{r, results='hide'}
df[,c(1,2)]
```

### delete one row with row number
delete row 5
```{r, results='hide'}
df[-5,]
```

### delete multiple row with row number
delete row 5,8,12,24
```{r, results='hide'}
df[-c(5,8,12,24),]
```

### delete the first 10 rows
```{r, results='hide'}
tail(df,nrow(df)-10)
```


### delete the last 10 rows
```{r, results='hide'}
head(df,nrow(df)-10)
```

### keep rows which column Girth > 12
```{r}
df[which(df$Girth > 12),]
```

### keep rows which column Girth > 12 and < 15 
```{r}
df$Girth >12
df$Girth < 15
df[df$Girth >12 & df$Girth < 15,]
```


### keep rows which column Girth < 10 or > 18 
```{r}
df[df$Girth < 10 | df$Girth > 18 ,]
```


### sort by column2: Height, increasing
```{r, eval=FALSE}
df[order(df$Height)] 
```


### sort by column2: Height, decreasing
```{r, eval=FALSE}
df[order(df$Height),decreasing = TRUE] 
```


### build a new data frame, nrow = 5, ncol = 3
```{r}
new.df <- data.frame(matrix(NA, nrow = 5, ncol = 3))
new.df
```

### set column names for new.df
```{r}
colnames(new.df) <- paste("col", seq(1,3),sep  = "_")
new.df
```

### merge df and new.df by row 
make sure column names are the same 
```{r}
colnames(new.df) <- colnames(df)
rbind(df, new.df)
```


There are many aspects of data frame manipulation, it is foundation of data analysis, many resources are online for unique quesitions. This page is just some basic functions. 
If you have any questions, welcome to contact me: fli105@syr.edu
