---
title: import csv, txt, excel files
author: Li Fu
date: '2019-10-10'
slug: import-csv-txt-excel-files
categories:
  - functions
tags:
  - import and output
---

# import csv
## Method1: choose file location manually 
```{r,eval=FALSE}
My.data <- read.csv(file.choose(), header = T)
```



## Method2: set working directory, then select file by file name
1. get woring directory
```{r,results='hide'}
getwd()
```

2. change working directory to folder where your r file locates
<p> Method1: click: "Session" - "Set Working Directory" - "Set Source File Location"</p>
<p> Method2: use code below </p>

```{r,eval=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

3. load in file from your working directory
<p>PS: this file is downloaded from yahoo finance, only for education use</p>
```{r, results='hide'}
My.data <- read.csv("./MSFT.csv")
```
"./" means file location from system to your working directory.

4. check do we load in correctly 
<p>Method1: If correctly, it will show in Environment(right hand side of RStudio)</p>
<p>Methods2: check header of the data frame</p>
```{r}
head(My.data, n = 5)
```

this function checks the first n row of My.data, if not given, by default, n = 6

Symmetrically, another function check last n rows, also, by default n = 6:
```{r}
tail(My.data, n = 3)
```

## NOTICE: Parameters for read.csv
full parameters are: 
```{r,eval=FALSE}
read.csv(file = "./MSFT.csv",
         header = T,
         sep = ",",
         quote = "\"",
         dec = ".",
         fill = TRUE,
         comment.char = "")
```

### header = T 
```{r}
head(read.csv("./MSFT.csv", header = T), n = 3)
```
<p>1,2,3 means row numbers</p>

<p>because in row 1, data is numeric for column 2-7, so data frame structure for column 2-7 are numeric, see below: </p>

```{r}
str(read.csv("./MSFT.csv", header = T))
```

### header = F
```{r}
head(read.csv("./MSFT.csv", header = F), n = 3)
```

<p> Now, row1 is header, so it is character, so column 2-7 becomes factor </p>

```{r}
str(read.csv("./MSFT.csv", header = F))
```

### csv file:
```{r, eval=FALSE}
sep = ","
```

### txt file:
```{r, eval=FALSE}
sep = " "
```

### escapye quotes
<p>rarely used in data input,but very useful for parsing data. </p>
```{r, eval=FALSE}
quote = "\"",

\'	ASCII apostrophe '
\"	ASCII quotation mark "
\n	newline
\r	carriage return
\t	tab
\b	backspace

```
<p> for more information visit:  https://stat.ethz.ch/R-manual/R-devel/library/base/html/Quotes.html


### some bizzar country use 71,908 represent 71.908
```{r, eval=FALSE}
dec = ","
```

### for regular number 71.908
usually you don't need to set this parameter, by default is "."
```{r, eval=FALSE}
dec = "."
```

# import txt
the only difference from import csv is change separation from comma to tab.

<p> data source: http://www.applied-maths.com/download/sample-data</p>
Antibiotics sample data - MIC data.txt
```{r}
read.csv(file = "./MIC data.txt", sep="\t")
```


# import xlx, xlsx
use a package 

<p>install</p>
```{r, eval=FALSE}
install.packages("xlsx")
```

 load 
```{r, eval=FALSE}
library("xlsx")
```

<p> data source: http://www.applied-maths.com/download/sample-data</p>
Antibiotics sample data - Zone diameter data.xls

```{r,eval=FALSE}
read.xlsx(file = "Zone diameter data.xls",header = T)
```

this package doesn't work on R Studio of mac, I don't know why, i don't like those technical problems,AHHHHHHHHHHHHHHHH, there is one post online might help you, but i failed based on his method, good luck:
https://zhiyzuo.github.io/installation-rJava/